DNSKEY Management

### 2012-12-03 paper/paper.tex
Minor improvements
Spellcheck

This section will expose the current deployment status of DNSSEC and
give the reader an idea about the current DNSSEC landscape before
going into the specific DNSKEY managment issues. Please refer to
section~\ref{sec:case-study} for more details on the situation of the
\verb|ch.| zone.

@@

We can see that DNSSEC is gradually being deployed and the number of
signed production zones grows rapidly (note the log-scale!). The rapid
increase of crawled DNSSEC zones mid-2008, so interprets
\cite{Osterweil09}, is due to a cache poisoning attack discovered in
summer 2008 \cite{dnsVuln}. During our research, we were unfortunately
unable to find an estimate of the number of (production) DNS zones in
the internet to estimate the percentage of DNSSEC penetration.

Contrary to the state at writing of \cite{Osterweil09}, the DNS
root-zone is signed since July 15, 2010 \cite{root-dnssec} and hence
serves as the global trust anchor. However, as of this writing,
data\footnote{\url{http://secspider.cs.ucla.edu/islands.html}}
gathered by \cite{secspider} suggests that more than half of the
deployed DNSSEC zones which are verifyable (i.e. are likely not to
have a spoofed key, see SecSpider in the next section or
\cite{Osterweil09} for details), do not have a fully linked
certificate chain up to the root zone.

@@

The Internet Software Consortium (ISC) still runs an inline TAR
\cite{iscDlv}, using the DNSSEC Lookaside Validation standard
\cite{RFC5074}. When a resolver needs to check the key of a zone
\verb|x| with this TAR, it makes a DNS request of type DLV to
\url{x.dlv.isc.org}. If it succeeds, the DLV record contains the
signature for the (hopefully matching) DNSKEY. The ISC inline TAR
requires manual addition of keys to the repository.

SecSpider \cite{secspider, Osterweil09} is another inline TAR, but
uses a different approach for key validation: Rather then entering and
signing public keys manually, it randomly queries DNSKEY entries from
different point in the world simultaniously and only enters it into
the TAR, if all the received keys match. This makes spoofing of a key
very difficult due to the spatial distribution and the
unpredictability of the queries.

Another type of TAR resides at the resolver: A statically configured
TAR stores keys locally at the resolver and hence needs not to issue an
additional query for keys when a new DNS request arrives. The
statically configured TAR may automatically poll keys asynchronously,
or is maybe just a bunch of manually configured trusted keys. As an
example of a statcially configured TAR, we have
Vantages\footnote{\url{http://www.vantage-points.org/}}, an addition
to a standard resolver, \cite{Osterweil09} which can poll keys from
different locations such as web pages, but also also other
vantage-enabled resolvers. Of course, the operater may also choose to
add trusted keys manually.

\section{Operations\wbjp}
\subsection{3Rs}
\subsection{Single admin}
\subsection{Multi admin}
\subsection{Disabling}

@@

\paragraph{Certificate Chain} According to a query on
\cite{secspider}, the \verb|ch.| TLD zone is signed and fully
veryfiable from the root zone anchor on downwards. The certificate
chain can hence fully be established and no separate TAR is required.

@@

Therefore, it is relatively simple to enable DNSSEC for a \verb|x.ch.| 
zone. While using the web-interface is certainly cumbersome when
having to deal with rollovers for a large number of domains, any major
provider may become a SWITCH Partner and can then switch over to EPP
which solves this issue.

>>>>

This section will expose the current deployment status of DNSSEC and
give the reader an idea about the current DNSSEC landscape before
going into the specific DNSKEY management issues. Please refer to
section~\ref{sec:case-study} for more details on the situation of the
\verb|ch.| zone.

@@

We can see that DNSSEC is gradually being deployed and the number of
signed production zones grows rapidly (note the log-scale!). The rapid
increase of crawled DNSSEC zones mid-2008, so interprets
\cite{Osterweil09}, is due to a cache poisoning attack discovered in
summer 2008 \cite{dnsVuln}. During our research, we were unfortunately
unable to find an estimate of the number of (production) DNS zones in
the Internet to estimate the percentage of DNSSEC penetration.

Contrary to the state at writing of \cite{Osterweil09}, the DNS
root-zone is signed since July 15, 2010 \cite{root-dnssec} and hence
serves as the global trust anchor. However, as of this writing,
data\footnote{\url{http://secspider.cs.ucla.edu/islands.html}}
gathered by \cite{secspider} suggests that more than half of the
deployed DNSSEC zones which are verifiable (i.e. are likely not to
have a spoofed key, see SecSpider in the next section or
\cite{Osterweil09} for details), do not have a fully linked
certificate chain up to the root zone.

@@

The Internet Software Consortium (ISC) still runs an inline TAR
\cite{iscDlv}, using the DNSSEC Lookaside Validation standard
\cite{RFC5074}. When a resolver needs to check the key of a zone
\verb|<X>| with this TAR, it makes a DNS request of type DLV to 
\url{<X>.dlv.isc.org}. If it succeeds, the DLV record contains the
signature for the (hopefully matching) DNSKEY. The ISC inline TAR
requires manual addition of keys to the repository.

SecSpider \cite{secspider, Osterweil09} is another inline TAR, but
uses a different approach for key validation: Rather then entering and
signing public keys manually, it randomly queries DNSKEY entries from
different point in the world simultaneously and only enters it into
the TAR, if all the received keys match. This makes spoofing of a key
very difficult due to the spatial distribution and the
unpredictability of the queries.

Another type of TAR resides at the resolver: A statically configured
TAR stores keys locally at the resolver and hence needs not to issue an
additional query for keys when a new DNS request arrives. The
statically configured TAR may automatically poll keys asynchronously,
or is maybe just a bunch of manually configured trusted keys. As an
example of a statically configured TAR, we have
Vantages\footnote{\url{http://www.vantage-points.org/}}, an addition
to a standard resolver, \cite{Osterweil09} which can poll keys from
different locations such as web pages, but also also other
vantage-enabled resolvers. Of course, the operator may also choose to
add trusted keys manually.

\section{Operations\wbjp}
\subsection{3Rs}
%% Talk about EPP or push burden to Case-Study
\subsection{Single admin}
\subsection{Multi admin}
\subsection{Disabling}

@@

\paragraph{Certificate Chain} According to a query on
\cite{secspider}, the \verb|ch.| TLD zone is signed and fully
verifiable from the root zone anchor on downwards. The certificate
chain can hence fully be established and no separate TAR is required.

@@

Therefore, it is relatively simple to enable DNSSEC for a \verb|<X>.ch.| 
zone. While using the web-interface is certainly cumbersome when
having to deal with rollovers for a large number of domains, any major
provider may become a SWITCH Partner and can then switch over to EPP
which solves this issue.
